What can Issues on GitHub and Google Code tell us about Bug Hazards in Android and Java?

### 2015-02-12 android-stacks.tex
section 2 - changes

In Java, exceptions are represented according to a class hierarchy, on which
 every exception is an instance of the Throwable class, and can be of three kinds: the checked exceptions
(extends Exception), the runtime exceptions (extends RuntimeException) and errors
(extends Error)~\cite{gosling2000java}. The checked exception received such name
 because they must be declared on the method's exception interface (i.e., a list of exceptions that a method 
might raise during its execution) and the compiler statically checks if
 appropriate handlers are provided within the system.
Both runtime exceptions and errors are also known as unchecked exceptions, because 
they do not need to be specified on method exception interface and do not trigger any 
compile time checking.

By convention an Error represents an unrecoverable condition which usually results
from failures detected by the Java Virtual Machine, such as OutOfMemoryError and
normally should not be handled inside the application. The user-defined exceptions 
can be either checked or runtime. The Java specification~\cite{gosling2000java} 
suggests that user-defined exceptions should be checked, because doing so 
the callers of a method will know about the exceptions that a method can throw, and then 
they can decide what to do about them. However, runtime exceptions can also be 
used to represent user-defined exceptional conditions.There is a long-lasting debate 
about the pros and cons of both approaches~\cite{javatut,stackoverlow,debate}
%\footnote{152 questions in Stackoverlow are related to this debate}.

The runtime exceptions are also implicitly thrown by the runtime environment when a program violates 
the semantic constraints of the Java programming language (e.g., out-of-bounds array index, divide-by-zero 
error, null pointer references).\footnote{Some programming languages react to such errors by peremptorily terminating the program; 
other programming languages allow similar approaches e.g.C\#; and others let the program to continue
 its execution in some situations such as the out-of-bounds array index e.g., C++. }  
The programs are not expected to handle such runtime exceptions signaled by the runtime environment ~\cite{gosling2000java}.

@@

In Java, once an exception is thrown, the runtime environment looks for the nearest enclosing exception handler
(in Java it is represented by the try-catch block), and unwinds the execution stack if necessary.
 Looking for the handler on the invocation stack is claimed to increase software reusability, 
since the invoker of an operation can handle it in a wider context ~\cite{miller1997issues}.

@@

\emph{IV- All exceptions explicitly thrown by a library/framework reusable code should be documented.}
(\cite{mandrioli1992advances,gosling2000java,wirfs2006toward,bloch2008effective}).
The exceptions thrown by a method are an important part of methods interface,
and is required to use the method properly. The checked exceptions are already
part of the  methods signature, and the method caller is aware of the checked
exceptions being thrown by it. According to~\cite{bloch2008effective}, it is
also wise to document  (either or on the exception interface or using @throws tag on Javadoc) 
the explicitly thrown runtime exceptions\footnote{This
excludes the implicitly signaled runtime exceptions related to programming
mistakes} as carefully as checked exceptions, e when developing
 library/framework reusable code. Doing so, the clients of such library/framework
will be aware of all the exceptions a method can throw and can design the code
to deal with them ~\cite{Robil00}.

@@

In this study we explore the domain quantitatively and highlight interesting cases by 
exploring cases qualitatively.  Figure~ref{fig:overview} gives an overview of the study, whose tasks are detailed next.

>>>>

\emph{\textbf{Exception Types.}} In Java, exceptions are represented according to a class hierarchy, on which
 every exception is an instance of the Throwable class, and can be of three kinds: the checked exceptions
(extends Exception), the runtime exceptions (extends RuntimeException) and errors
(extends Error)~\cite{gosling2000java}. The checked exception received such name
 because they must be declared on the method's exception interface (i.e., a list of exceptions that a method 
might raise during its execution) and the compiler statically checks if
 appropriate handlers are provided within the system.
Both runtime exceptions and errors are also known as unchecked exceptions, because 
they do not need to be specified on method exception interface and do not trigger any 
compile time checking.

By convention, instances of Error represent  unrecoverable conditions which usually results
from failures detected by the Java Virtual Machine due to resource limitations such as OutOfMemoryError;
normally they cannot be handled inside the application.

Instances of RuntimException are implicitly thrown by Java runtime environment when a program violates 
the semantic constraints of the Java programming language (e.g., out-of-bounds array index, divide-by-zero 
error, null pointer references). Some programming languages react to such errors by peremptorily terminating the program; 
other programming languages allow similar approaches e.g.C\#; and others let the program to continue
 its execution in some situations such as the out-of-bounds array index e.g., C++. 
The programs are not expected to handle such runtime exceptions signaled by the runtime environment according 
to the Java Specification ~\cite{gosling2000java}.

The user-defined exceptions can be either checked or runtime. There is a long-lasting debate 
about the pros and cons of both approaches~\cite{javatut,stackoverlow,debate}
%\footnote{152 questions in Stackoverflow are related to this debate}. 
Section ~\ref{sec:best} presents
a set of best practices related to each exception type.

@@

\emph{\textbf{Exception Propagation.}} In Java, once an exception is thrown, 
the runtime environment looks for the nearest enclosing exception handler
(in Java it is represented by the try-catch block), and unwinds the execution stack if necessary.
 Looking for the handler on the invocation stack is claimed to increase software reusability, 
since the invoker of an operation can handle it in a wider context ~\cite{miller1997issues}.

@@

\emph{IV- All exceptions explicitly thrown by reusable code should be documented.}
(\cite{mandrioli1992advances,gosling2000java,wirfs2006toward,bloch2008effective}).
The exceptions thrown by a method are an important part of methods interface,
and is required to use the method properly. The checked exceptions are already
part of the  methods signature, and the method caller is aware of the checked
exceptions being thrown by it. According to~\cite{bloch2008effective}, it is
also wise to document (either or on the exception interface or using @throws tag on Javadoc) 
the explicitly thrown runtime exceptions as carefully as checked exceptions. 
When mentioning reffering to `` explicit" thrown exceptions
we  exclude the implicitly signaled runtime exceptions related to programming
mistakes. Such practice is mostly needed when developing library/framework 
code reusable code - as the developers do not have access to the source code. 
Doing so, the clients of such library/framework
will be aware of all the exceptions a method can throw and can design the code
to deal with them ~\cite{Robil00}.

@@

In this study we explore the domain quantitatively and highlight interesting cases by 
exploring cases qualitatively.  Figure~\ref{fig:overview} gives an overview of the study, whose tasks are detailed next.
